### 2011-06-30 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\documentclass[a4paper,12pt,oneside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}

@@

Title:  [the master thesis title in English]

@@

Keywords: [3-5 keywords in English]

@@

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

@@

TODO talk about key definition from KfXML

@@

TODO talk about FIDAX

@@

@@

TODO what is heuristics (link wise books), what is metaheuristics (we will be using them)

@@

@@

\subsubsection{Truncated Branch & Bound}

@@

@@

\subsubsection{Remove Random}

@@

@@

@@

\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}

@@

%%% Tabulky v diplomové práci, existují-li.
\chapwithtoc{List of Tables}
\listoftables

@@

\chapwithtoc{Attachments}
\openright
\end{document}

>>>>

\documentclass[a4paper,12pt,oneside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage{appendix}

@@

Title:  Inference of XML Integrity Constraints

@@

Keywords: XML, ID attributes, inference

@@

\chapwithtoc{Preface}

@@

TODO talk about key definition from \cite{keX}

@@

According to the article \cite{fidax}, ...

TODO talk about FIDAX
To the best of our knowledge, there are no other articles dealing with this problem

TODO talk about Fajt - but that's different, that's keys

@@

TODO other approaches to max IS

@@

TODO what is heuristics (link wise books), what is metaheuristics (we will be using them)
TODO mention things like Taboo search

TODO we will be working with heus striving to do the following: input is a list of AMs, they have their weight, we try to find a non-conflicting subset which maximizes the weight

@@

TODO construction heuristics are heus that provide us with at least some solution.

@@

\subsubsection{Truncated Branch \& Bound}

@@

\subsubsection{Identity}

TODO trivial trivial

@@

\subsubsection{Random Remove}

@@

\subsubsection{Hungry}

\subsubsection{Mutation}

TODO

\subsubsection{Crossover}

TODO

\subsubsection{Local Branching}

TODO

@@

\section{Experimental Data}

@@

\chapwithtoc{Conclusion}

TODO conclusion

@@

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables

@@

\appendix

\openright
\addcontentsline{toc}{chapter}{Appendices}

\chapter{jInfer}

\end{document}
